% Resume template taken from RPI (http://www.rpi.edu/dept/arc/training/latex/resumes/)
% Resume #9a
% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Seyitcan K. Ucin}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{(321)-948-9049}
 \moveleft.5\hoffset\centerline{sucin@princeton.edu}
 \moveleft.5\hoffset\centerline{}
 \moveleft.5\hoffset\centerline{1179 Frist Center}
 \moveleft.5\hoffset\centerline{Princeton University}
 \moveleft.5\hoffset\centerline{Princeton, NJ 08544}




\begin{resume}
 
\section{OBJECTIVE}  A position in the field of data analysis with special 
                interests in management systems, quantitative finance, and econometrics. 
 

\section{EDUCATION} {\sl Bachelor of Science in Engineering,} Operations Research \& Financial Engineering \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                Princeton University, Princeton, NJ, expected June 2020\\
                Certificates: Statistics \& Machine Learning, Applications of Computing\\              

                West Orange High School, Winter Garden, FL, May 2016 \\
                {\sl Salutatorian, Science Department Award, QuestBridge 
                Finalist, National AP Scholar, Captain of Robotics Team, 
                Vice President of Speech \& Debate Team}
 
 
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} Microsoft Office Suite,
                C, C++, Java, Python, Ruby, MATLAB \\
 
\section{EXPERIENCE} {\sl IT Support} \hfill Fall 2016 \\
                School of Architecture, 
                Princeton University, Princeton, NJ 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Provided AV support for lectures given by faculty
                 and guest lecturers.
                \item   Developed API's to link lecture hardware (projectors,
                sound equipment) to software interfaces in every lecture hall.
                \end{itemize}
 
                {\sl Lab Technician} \hfill            Fall 2016 \\
                Chemistry Department, Princeton, University, Princeton, NJ
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Provided assistance in the chemistry laboratory by
                 mixing solutions and preparing laboratory materials for 
                 general chemistry.
                 \end{itemize} 

                {\sl Research Intern} \hfill        Summer 2015 \\
                Laser \& Plasma Laboratory, University of Central Florida, Orlando, FL
                  \begin{itemize}
                   \item Research in multi-terawatt ultrafast laser spectroscopy 
                   and its applications in detecting explosives and other harmful 
                   materials to improve homeland security. Research was part of 
                   the US Army Outreach Program and was funded by the Army 
                   Research Office. Principal Investigator: Dr. Martin Richardson.
                   \end{itemize} 
 

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Elected {\it Captain}, West Orange Robotics Team \\
            Elected {\it Vice President}, West Orange Speech \& Debate Team \\
             {\it Writer}, The Princeton Progressive\\
 

\end{resume}
\end{document}




